### 2018-05-18 conclusion.tex
Paper outline finished

% The main conclusions of the study may be presented in a short Conclusions
% section, which may stand alone or form a subsection of a Discussion or Results
% and Discussion section.

>>>>

Condensed copy-paste of the thesis conclusion.
\begin{itemize}
    \item Full-core model which is better the most exists. Importance of full-core approach for multi-region designs.
    \item K-eff dynamics and explanation of this dynamics.
    \item Spectral shift explanation.
    \item Why spectral shift causes safety parameters worsening and power profile changes.
    \item $^{232}$Th rate is in a good agreement with references.
\end{itemize}

### 2018-05-18 introduction.tex
Paper outline finished

\section{Introduction}
% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.

>>>>

\section{Introduction}
% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.
\begin{itemize}
	\item Background and motivation from the thesis. 
	\item Brief \gls{MSR} overview and 1 paragraph history. 
	\item \gls{MSBR} advantages. Objectives from the thesis. 
	\item Changed simulation time 40 years (or more). 
	\item Figure 2.3: Isotopic build-up in $^{232}$Th and $^{238}$U breeding systems. 
	\item Literature review from Section 2.3 without multiphysics + existing full-core simulations (Park et al., Skirpan et al.)
\end{itemize}

### 2018-05-18 results.tex
Paper outline finished

% Results should be clear and concise.

>>>>

\begin{itemize}
  \item K-eff over 40 years of simulation with $<$15pcm uncertainty.
  \item Dynamics isotope composition from initial to equilibrium composition.
  \item Dynamics of fissile vs non-fissile isotopes over 40 years.
  \item Neutron spectrum for both states and separately for Zone I and Zone II (probably, even Zone II-A and II-B).
  \item Power distribution plot (without breeding, too much pics).
  \item Control rod worth \& Six factor analysis \& temperature coefficients.
  \item $^{232}$Th refill rate.
  \item Bried discussion (2-3 paragraph).
\end{itemize}
